---
title: "p8105_hw1_kp3127"
output: html_document
date: "2025-09-19"
---

#problem 1
```{r}
library("tidyverse")
library("moderndive") 
data("early_january_weather")
names(early_january_weather)
```

The `early_january_weather` dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns of hourly weather observations.

Key variables include:  
**time_hour**, which records the date and hour of each 
measurement (the first entry is `r early_january_weather$time_hour[1]`).  
**temp**, the air temperature in degrees Fahrenheit with a mean of 
`r round(mean(early_january_weather$temp, na.rm = TRUE), 1)` °F.  
**humid**, the relative humidity with a mean of `r round(mean(early_january_weather$humid, na.rm = TRUE), 2)`.  
Other variables provide information on wind speed, precipitation, etc.

```{r echo=FALSE}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point()
```

```{r echo=FALSE}
ggsave("temp_vs_time.png")
```

